\section{Abstract}
\label{se:abstract}
\subsection{Research Area}
IMO has in the second generation intact stability criteria \cite{imo_second_nodate} addressed six possible dynamic stability failures. Having sufficient roll damping is very important in these failure modes, especially: \emph{Parametric roll}, \emph{Dead Ship condition} and \emph{Excessive acceleration}.
		
\subsection{Purpose, Objective}
Many crucial decisions that are made during the early design stage, regarding the main dimensions of ships, are based on predictions where the roll damping has been calculated with semi-empirical methods. The accuracy of these methods, when applied to modern ship designs, is however quite uncertain. Söder et al. \cite{soder_ikeda_2019} has for instance investigated Ikeda’s method for modern volume carriers where it was concluded that the speed dependence of the bilge keels damping was underestimated.

The accuracies of these methods are investigated in this project and it is investigated if the methods can be improved.

\subsection{Methods}
The accuracy will be investigated by benchmarks of a large number \textcolor{red}{(how many?)} of roll decay model tests. Machine Learning techniques are used to investigate if the best semi-empirical methods can be improved.

\begin{itemize}
	\item Develop methods to determine roll damping coefficients using parameter identification techniques on roll decay model test results. The methods should be general enough to be run automatically on a large number of model tests.
    \item Use the developed methods to build a roll damping data base.
    \item Verify existing semi-empirical formulas using the roll damping data base.
    \item Improve existing semi-empirical formulas using machine learning on the roll damping data base.
\end{itemize}		
			
			
\subsection{Simulations/Analysis}

			
\subsection{Results}
The accuracy of existing semi-empirical formulas to predict roll damping will be estimated based on statistical data from the roll damping data base.

Improvements of existing semi-empirical formulas will be proposed. 